Bootstrap learning via modular concept discovery

### 2013-04-22 drafts/ijcai2013/camera_ready/Dechter.IJCAI13.CameraReady.tex
Changes to first paragraph of introduction.

\section{Introduction}
A central question for AI is how to create intelligent agents without
building in vast amounts of pre-specified knowledge that is tailored
to one domain or another. Any attempt to solve this problem must
contend with the fact that the less an agent knows about solving
problems in a domain, the worse its attempts are, and, therefore, the
less informative they are about how to solve subsequent problems.

For example, imagine you know nothing about electronics but are
supplied with a collection of circuit elements and asked to build a
useful device: your initial attempts will be uniformly
ineffective. If, on the other hand, you know the basics, you are far
more likely to generate devices that are somewhat successful and on
whose basis you might improve your skills.

@@

Domain specific knowledge provides this structure. In local search, it
defines the similarity metric between solutions; in heuristic search
it provides the heuristic. Here we ask how to bootstrap domain
specific knowledge and extract structure from the space of possible
solutions by attempting to solve multiple related problems in a given
domain at once. Our approach is motivated by the observation that many
interesting problems -- such as discovering scientific theories,
developing new technologies, learning to play a new instrument -- have
solutions that are naturally specified as programs.

>>>>

\section{Introduction}
A central question for AI is how to create intelligent agents without
building in vast amounts of pre-specified knowledge that is tailored
to one domain or another. This is generally accomplished by a learning
algorithm that uses past experience to improve future performance. The
problem is that if past problem solving attempts entirely missed the
mark, their failures are unlikely to shed light on will work and what
will not. Such uninformative solutions, however, vastly outnumber the
rest, and our uninformed agent has no way to know which solutions will
be informative and which will not. Thus, our learning algorithms must
contend with a bootstrapping problem: the less an agent knows to begin
with, the harder it is to learn from experience.

For example, imagine you know nothing about electronics but are
supplied with a collection of circuit elements and asked to build a
number of canonical useful devices, such as a digital adder, an
op-amp,, etc. Your initial attempts will be uniformly ineffective. If,
on the other hand, you know the basics of circuit design, you are far
more likely to generate devices that are somewhat successful and on
whose basis you might improve your designs and your design skills.

@@

This structure derives from domain specific knowledge. In local
search, domain knowledge provides the similarity metric between
solutions; in heuristic search it provides the heuristic. Here we ask
how to bootstrap domain specific knowledge and extract structure from
the space of possible solutions by attempting to solve multiple
related problems in a given domain at once. Our approach is motivated
by the observation that many interesting problems -- such as
discovering scientific theories, designing new technologies, learning
a skill such as playing an instrument or cooking -- have solutions that
are naturally specified as programs.
